Interpretable Deepfake Voice Detection: A Hybrid Deep-Learning Model and Explanation Evaluation

### 2025-03-08 draft.tex
add confirmation

A promising direction for future work would be integrating this method into different domains where feature-based local explanations have the potential to be effective. In such application domains, we could further validate both the accuracy and the usefulness of the generated explanations as well as the selected features using our proposed metrics. Additionally, it would be valuable to compare findings from a user study on the generated explanations with our metric-based evaluation.
	\newpage
	\sloppy
	\printbibliography
\end{document}

>>>>

A promising direction for future work would be integrating this method into different domains where feature-based local explanations have the potential to be effective. In such application domains, we could further validate both the accuracy and the usefulness of the generated explanations as well as the selected features using our proposed metrics. Additionally, it would be valuable to compare findings from a user study on the generated explanations with our metric-based evaluation.
	\newpage
	\sloppy
	\printbibliography
	\newpage
	\section{Erklärung}
	Hiermit versichere ich, dass ich die vorliegende Arbeit selbstständig, insbesondere auch nicht mit Hilfe einer KI-Software, angefertigt habe. Ich habe ausschließlich die angegebenen Hilfsmittel und Quellen benutzt; das betrifft auch Quellen und andere Informationen aus dem Internet. Alle Stellen, die wörtlich oder sinngemäß aus veröffentlichten und nicht veröffentlichten fremden Schriften entnommen wurden, sind als solche kenntlich gemacht.

	Die Paragraphen der für mich geltenden Prüfungsordnungen, die etwaige Betrugs-versuche betreffen, habe ich zur Kenntnis genommen.

	Der Speicherung meiner Abschlussarbeit zum Zweck der Plagiatsprüfung stimme ich zu. Ich versichere, dass die elektronische Version mit der gedruckten Version inhaltlich übereinstimmt. \\ \\ \\ \\

	\hline
	Datum \quad \quad \quad \quad \quad \quad \quad \quad Unterschrift
\end{document}
